\sout{Rare-event sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body} \ZZ{Numerical study of extreme mechanical efforts exerted by a turbulent flow on a bluff body by direct and rare-event sampling techniques}

### 2020-02-05 jfm/draft_p2_jfm.tex
Update final paragraph on AMS

Our results indicate that the \ac{ams} cannot be straightforwardly applied to convective flows past obstacles,
in which the timescale of extreme events (here a drag fluctuation) is smaller than the duration required
for trajectories to separate under the influence of turbulence.
The the author's knowledge, this result is the first evidence of the limitations of splitting approaches such as the \ac{ams} for complex systems, for which the only available choice for the score function displays a memory. \textbf{Do we agree on this last paragraph?}

>>>>

Our results indicate that the \ac{ams} does not work with this simple choice of score function.
Better results may be obtained by using a different score function, but at this stage we do not know how to build such a score function for this specific problem.
